Expert-in-the-Loop Causal Discovery

### 2024-05-02 paper/main.tex
Typo fix

\begin{abstract}
	Causal discovery is a fundamental problem in causal inference, and numerous algorithms have been developed to address it. However, their adoption in applied disciplines  as been limited, possibly due to a lack of confidence in these algorithms stemming from them making obvious mistakes, and the difficulties in choosing the right algorithm for specific datasets. Consequently, in applied disciplines, these causal Directed Acyclic Graphs (DAGs) are predominantly constructed manually based on domain expertise. However, some researchers do validate and modify their DAGs by testing them against data through Conditional Independence (CI) tests. To assist researchers in this task, we have developed a web-based tool to aid researchers in constructing, validating, and modifying DAGs. The tool uses effect size measures from CI testing to iteratively suggest potential additions or removals of edges between variables, while allowing experts to choose between recommendations and specify the directionality of the edges. Furthermore, we introduce a novel effect size measure for mixed data, enabling the tool to work for any combination of variable types. Empirically, we show that taking a greedy approach on the tool's recommendations can perform comparably to causal discovery algorithms, provided that the expert correctly determines the direction of the edges in at least one out of three cases, with performance improving as accuracy increases.
\end{abstract}

>>>>

\begin{abstract}
	Causal discovery is a fundamental problem in causal inference, and numerous algorithms have been developed to address it. However, their adoption in applied disciplines  has been limited, possibly due to a lack of confidence in these algorithms stemming from them making obvious mistakes, and the difficulties in choosing the right algorithm for specific datasets. Consequently, in applied disciplines, these causal Directed Acyclic Graphs (DAGs) are predominantly constructed manually based on domain expertise. However, some researchers do validate and modify their DAGs by testing them against data through Conditional Independence (CI) tests. To assist researchers in this task, we have developed a web-based tool to aid researchers in constructing, validating, and modifying DAGs. The tool uses effect size measures from CI testing to iteratively suggest potential additions or removals of edges between variables, while allowing experts to choose between recommendations and specify the directionality of the edges. Furthermore, we introduce a novel effect size measure for mixed data, enabling the tool to work for any combination of variable types. Empirically, we show that taking a greedy approach on the tool's recommendations can perform comparably to causal discovery algorithms, provided that the expert correctly determines the direction of the edges in at least one out of three cases, with performance improving as accuracy increases.
\end{abstract}
